Global code motion of congruent instructions

### 2017-04-18 paper.tex
algos

\begin{verbatim}
computing barriers:
for each basic-block B in a function:
  barrier_found = false
  for each instruction I in B:
    if I does not guarantee progress:
      mark I as a barrier instruction
      barrier_found = true
      break;

@@

\begin{verbatim}
computing downward-safety of hoistable instructions at hoist-point
  Worklist = list of all basic-blocks of hoistable instructions
  for each basic-block B in the dominator tree starting at hoist-point:
    if Worklist is empty, return false // Path exists! not downward safe
    if B is in Worklist:
      remove B from worklist
      remove subtree with root at B // Available at B => downward safe from B
    if B is a leaf basic-block, return false  // Path exists! not downward safe
    if B dominates hoist-point, return false  // Back edge
  return true
\end{verbatim}

@@

\begin{verbatim}
int doCodeHoisting()
  For each value number VN with 2 or more instructions (I1, I2, ..., Ik)
    sort the instructions according to DFSIn numbers
    if first two I1, I2 are hoistable and if they are downward-safe at hoist-point
       and if they are profitable to be hoisted at hoist-point
      proceed to check ability to hoist of subsequent instruction with same VN
    else
      proceed to check if I2 and I3 (if available) can be hoisted
  For each set of instructions (I1, ..., Ik) with same VN that can be hoisted:
    move the first one I1 to the hoist-point
    update the use of all other candidates (I2, ..., Ik) to refer to I1
    remove all other instructions (I2, ..., Ik)
    if I1 has memory references (a load, store, call, etc.)
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics
  return number of hoisted instructions
\end{verbatim}

@@

\begin{verbatim}
void doCodeSinking()
  For each value number VN with 2 or more instructions
    if there are two instructions with same immediate successor as post-dominator
      if both are only used in the same PHI-node (PN) of the successor
        if both have dependencies that are available at the sink point
           // available or can be made available by rematerialization
           mark VN as sinkable
  For each pair (I1, I2) of sinkable instructions
    Move I1 to the sink point
    // the sink point is just after all the PHI-nodes in the post-dominator
    update all the uses of PHI node (PN) with I1
    Remove I2 and PN
    if I1 is a memory reference:
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics
\end{verbatim}

>>>>

\begin{verbatim}
// Compute barriers for both hoistable and sinkable
// candidates.
void compute_barriers()
  for each basic-block B in a function:
    barrier_found = false
    for each instruction I in B:
      if I does not guarantee progress:
        mark I as a barrier instruction
        barrier_found = true
        break;

@@

\begin{verbatim}
// Compute downward safety of hoistable instructions at hoist-point
void compute_downward_safety()
  Worklist = list of all basic-blocks of hoistable instructions
  for each basic-block B in the dominator tree starting at hoist-point:
    if Worklist is empty, return false // Path exists! not downward safe
    if B is in Worklist:
      remove B from worklist
      remove subtree with root at B // Available at B => downward safe from B
    if B is a leaf basic-block, return false  // Path exists! not downward safe
    if B dominates hoist-point, return false  // Back edge
  return true
\end{verbatim}

@@

\begin{verbatim}
int doCodeHoisting()
  // Collect hoistable candidates
  For each value number VN with 2 or more instructions (I1, I2, ..., Ik)
    sort the instructions according to DFSIn numbers
    if first two I1, I2 are hoistable and if they are downward-safe at hoist-point
       and if they are profitable to be hoisted at hoist-point
      proceed to check ability to hoist of subsequent instruction with same VN
    else
      proceed to check if I2 and I3 (if available) can be hoisted

  // Do the code hoisting and update statistics
  For each set of instructions (I1, ..., Ik) with same VN that can be hoisted:
    move the first one I1 to the hoist-point
    update the use of all other candidates (I2, ..., Ik) to refer to I1
    remove all other instructions (I2, ..., Ik)
    if I1 has memory references (a load, store, call, etc.)
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics

  return number of hoisted instructions
\end{verbatim}

@@

\begin{verbatim}
void doCodeSinking()
  // Find sinkable instructions
  For each value number VN with 2 or more instructions
    if there are two instructions with same immediate successor as post-dominator
      if both are only used in the same PHI-node (PN) of the successor
        if both have dependencies that are available at the sink point
           // available or can be made available by rematerialization
           mark VN as sinkable

  // Sink the instructions and update statistics
  For each pair (I1, I2) of sinkable instructions
    Move I1 to the sink point
    // the sink point is just after all the PHI-nodes in the post-dominator
    update all the uses of PHI node (PN) with I1
    Remove I2 and PN
    if I1 is a memory reference:
      update MemorySSA of I1
      update MemorySSA of removed instructions to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics

  return number of sinked instructions
\end{verbatim}
